Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-10-06 paper-correlations.tex
Map approach (2/2)

\subsection{Lineal-path function}

Since the method for calculating $l_2$ using the FFT is unknown,
we use the direct approach:
scan the image in each selected direction.
\textcolor{red}{[czech paper]} uses this method,
but our approach saves porosity when rotating the image.
The top-level algorithm is described below, 
and the details are placed in the appendix.

\begin{algorithmic}[1]
  \Procedure{l2\_map}{$a, periodic, directions$}
    \ForAll{$direction \in directions$}
      \State $rotated \gets rotate(a, direction, periodic)$
      \State $l2[direction] \gets scan\_l2(aligned, periodic)$
    \EndFor
    \State \textbf{return} $l2$
  \EndProcedure
\end{algorithmic}

Align and rotate are simple operations with linear computational complexity.
Therefore, the complexity of the entire algorithm depends linearly 
on the number of directions and on the size of the image.

\subsubsection{Total number of trials}
$auto\_correlation$ and $cross\_correlation$ return non-negative number
of success trials \cref{eq:probability}.
To compute probability we need to count total number of trials.
This value depends on boundary conditions.
We realize two types: periodic and non-periodic (flat).

\begin{algorithmic}[1]
  \Procedure{total}{$a, periodic$}
    \State $m, n \gets size(a)$
    \If{periodic}
      \ForAll{$i \in range(0, m - 1)$}
        \ForAll{$j \in range(0, n - 1)$}
          \State $total[i, j] \gets m \cdot n$
        \EndFor
      \EndFor
    \Else
      \ForAll{$i \in range(-m + 1, m - 1)$}
        \ForAll{$j \in range(-n + 1, n - 1)$}
          \State $i' \gets mod(i, 2m - 1)$
          \State $j' \gets mod(j, 2n - 1)$
          \State $total[i', j'] \gets |m - i| \cdot |n - j|$
        \EndFor
      \EndFor
    \EndIf
    \State \textbf{return} $total$
  \EndProcedure
\end{algorithmic}

Described function is for 2D images,
for 1D and 3D images realization is similar.

if n is the number of pixels, then computational complexity
of this funciton is $O(n)$.

>>>>

Using \cref{eq:cross-ft} we obtain an algorithm for surface-void function:
\begin{algorithmic}[1]
  \Procedure{$F_{sv}$}{$A, phase, periodic$}
  \If{$\neg periodic$}
    \State $A \gets zeropad(A)$
  \EndIf
  \State $A^{(phase)} \gets I^{(phase)} (A)$
  \State $A^{(void)} \gets I^{(void)} (A)$
  \State $E_A \gets E * A^{(phase)}$
  \State $\hat{E}_A \gets F[E_A]$
  \State $\hat{A}^{(void)} \gets F[A^{(void)}]$
  \State $\hat{F}_{sv} \gets \hat{E}_A \overline{\hat{A}^{(void)}} / N$
  \State \textbf{return} $F^{-1} [\hat{F}_{sv}]$
  \EndProcedure
\end{algorithmic}

\textcolor{red}{Lineal path function?}
